Journey: A Study of Scalabilty of Memory Management in Linux

### 2017-05-03 paper.tex
Added acknowledgements section
reordered sections in results
Removed a couple of figures; acknowledgements

\begin{figure}[t]
    \includegraphics[width=\columnwidth]{figures/swap_time_cont}
    \caption{Time to touch a page while swapping for \texttt{cont} benchmark.
    Notice that the y-scale is logarithmic.\label{fig:swap_time_cont}}
\end{figure}

\begin{figure}[t]
    \includegraphics[width=\columnwidth]{figures/swap_time_rand}
    \caption{Time to touch a page while swapping for \texttt{rand}
    benchmark.\label{fig:swap_time_rand}}
\end{figure}

@@

>>>>

%\begin{figure}[t]
%    \includegraphics[width=\columnwidth]{figures/swap_time_cont}
%    \caption{Time to touch a page while swapping for \texttt{cont} benchmark.
%    Notice that the y-scale is logarithmic.\label{fig:swap_time_cont}}
%\end{figure}
%
%\begin{figure}[t]
%    \includegraphics[width=\columnwidth]{figures/swap_time_rand}
%    \caption{Time to touch a page while swapping for \texttt{rand}
%    benchmark.\label{fig:swap_time_rand}}
%\end{figure}

@@

\section{Acknowledgements}

We would like to thank Mitchell Manar, Akhil Guliani, Jing Liu, and Mayur
Cherukuri for their useful and insightful reviews on our draft. We hope they
enjoyed our jokes. Also, we would like to thank Mike Swift for his mentorship
and guidance.
